*Symbiodinium* communities in reef corals of St. John, U.S.V.I. (2012)

### 2016-09-07 analysis/STJ2012_analysis.Rmd
new labels ("Subtype2") on network vertices

# Label clades and subtypes for filtered phyloseq object tax_tables
get.st <- function(df) {
  within(df, {
    Clade <- substr(hit, 1, 1)
    Subtype <- gsub(hit, pattern="_[A-Z]{2}[0-9]{6}", replacement="")
    Subtype <- gsub(Subtype, pattern="_multiple", replacement="")
    Subtype2 <- ifelse(as.numeric(sim)==100, Subtype,
                       paste0("[", rep(rle(sort(Subtype))$values, times=rle(sort(Subtype))$lengths), "]^", 
                              unlist(lapply(rle(sort(Subtype))$lengths, seq_len)))[order(order(Subtype))])
    Subtype <- ifelse(as.numeric(sim)==100, Subtype, paste("*", Subtype, sep=""))
  })
}

@@

# Clade overview
Here the composition of each sample is plotted as a horizontal bar, sorted by species and shore. Each segment of the bar represents an individual OTU and is colored by clade. This plot is a nice overview of the whole dataset but only provides coarse information at the clade level.
```{r cladecomp97bs, cache=T, fig.height=6, fig.width=4}
cladeAbund <- aggregate(data.frame(RelAbund=rowSums(otu_table(phy97bs.f.p))),
                        by=list(Clade=data.frame(tax_table(phy97bs.f.p))$Clade), FUN=sum)
cladeAbund$Prop <- prop.table(cladeAbund$RelAbund)

@@

cladeAbund$Notus <- table(data.frame(tax_table(phy97bs.f.p))$Clade)

par(mfrow=c(1,1), mar=c(2, 1.5, 2, 5), lwd=0.1, cex=0.7)
# Plot composition of 97% within-sample OTUs colored by clade
composition(phy97bs.f.p, col=taxcolors[factor(data.frame(tax_table(phy97bs.f.p))[order(data.frame(tax_table(phy97bs.f.p))$Subtype), ]$Clade, levels=c("A","B","C","D","F","G"))], legend=T)
# Plot composition of 97% within-sample OTUs colored by OTU
#composition(phy97bs.f.p, col=rainbow(ntaxa(phy97bs.f.p)), legend=F)

>>>>

# Label clades and subtypes for filtered phyloseq object tax_tables
get.st <- function(df) {
  within(df, {
    Clade <- substr(hit, 1, 1)
    Subtype <- gsub(hit, pattern="_[A-Z]{2}[0-9]{6}", replacement="")
    Subtype <- gsub(Subtype, pattern="_multiple", replacement="")
    Subtype2 <- ifelse(as.numeric(sim)==100, Subtype,
                       paste0("'[", rep(rle(sort(Subtype))$values, times=rle(sort(Subtype))$lengths), "]'^", 
                              unlist(lapply(rle(sort(Subtype))$lengths, seq_len)))[order(order(Subtype))])
    #Subtype <- ifelse(as.numeric(sim)==100, Subtype, paste("*", Subtype, sep=""))
  })
}

@@

# Clade overview
Here the composition of each sample is plotted as a horizontal bar, sorted by species and shore. Each segment of the bar represents an individual OTU and is colored by clade. This plot is a nice overview of the whole dataset but only provides coarse information at the clade level.
```{r cladecomp, cache=T, fig.height=3, fig.width=4}
cladeAbund <- aggregate(data.frame(RelAbund=rowSums(otu_table(phy97bs.f.p))),
                        by=list(Clade=data.frame(tax_table(phy97bs.f.p))$Clade), FUN=sum)
cladeAbund$Prop <- prop.table(cladeAbund$RelAbund)

@@

cladeAbund$Notus <- table(data.frame(tax_table(phy97bs.f.p))$Clade)
```

```{r cladecomp_bysample, cache=T, fig.height=6, fig.width=4}
par(mfrow=c(1,1), mar=c(2, 1.5, 2, 5), lwd=0.1, cex=0.7)
# Plot composition of 97% within-sample OTUs colored by clade
composition(phy97bs.f.p, col=taxcolors[factor(data.frame(tax_table(phy97bs.f.p))[order(data.frame(tax_table(phy97bs.f.p))$Subtype), ]$Clade, levels=c("A","B","C","D","F","G"))], legend=T)
# Plot composition of 97% within-sample OTUs colored by OTU
#composition(phy97bs.f.p, col=rainbow(ntaxa(phy97bs.f.p)), legend=F)
